COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-06-24 main.tex
Typos and small suggestions.

Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure. Features such as gaps and asymmetries 
\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
diagnostics for the physical processes that drive the evolution of the disks. In many gas-rich systems, these gap features are argued to indicate the 
presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
interactions can have strong effects on the resulting morphologies \citep{2018ApJ...866..110D}. In gas-poor/debris systems, a giant perturber can also influence 
the structure of the dust continuum emission. For example, a misaligned giant planet can produce nonaxisymmetric features such as warps 
\citep{2001A&A...370..447A}, highly eccentric perturbers can produce structures through secular interactions 
\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}, and mean motion resonances (MMRs) can open gaps
\citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

@@

This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive the evolution 
of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:sims} we provide an overview of the N-body code 
used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses 
and eccentricities. Section \ref{sec:results} presents the results of these simulations and we use the collision statistics to generate synthetic dust 
emission profiles that would be detected with observing facilities like ALMA. Next, we show in section \ref{sec:constrain} that a characteristic bump 
or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
planet. We discuss the potential of using this feature to place and upper or lower on the mass and eccentricity of the planet and conclude in section 
\ref{sec:conclusions}.

@@

The most direct and widespread effect that a giant perturber will have on a planetesimal disk is through secular forcing of the 
eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time-independent 
forced value, given by \citep{1999ApJ...527..918W} as

@@

\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, 
respectively. $e_{g}$ and $\varpi_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a 
Laplace coefficient given by \citep{2000ssd..book.....M} as

@@

\noindent where $\lambda = \varpi + M$ is the mean longitude of a body. For bodies in resonance, the critical angle will librate around an 
equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
pendulum. Variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{2000ssd..book.....M}. An important 
point to note, which we will come back to later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of 
the $\phi$. For second and higher order resonances, the maximum libration width is given by

@@

\noindent where n, a and e are the mean motion, semimajor axis and eccentricity of the unperturbed body. $C_{r}$ is a constant defined by 
$m'/m_{c} n \alpha f_{d}(\alpha)$, where $\alpha$ = $a/a'$ and $f_{d}$ is the resonant part of the disturbing function. For an interior second-order 
resonance,

@@

In total, five simulations are run, which are listed in table \ref{tab:sims}. The first is a `nominal' case, in which the perturbing planet's mass and 
eccentricity are set to that of Jupiter's. In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the 
eccentricity (mass) is held at the nominal value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The 
planetesimal disk extends from 2.2 to 3.8 AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU 
and the 3:1 at 2.5 AU. The planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}

@@

For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/
G M_{\odot}}$. All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr. This is roughly 3\% of an orbital dynamical time at 
the inner edge of the planetesimal disk. From numerical tests with {\sc ChaNGa}, we have found that this time step size preserves 
the symplectic nature of the integration without being too computationally expensive. Although using $\Delta T$ = 0.01 yr keeps the 
integration symplectic, we find that a small amount of artificial precession is produced. This is most noticeable at the inner edge of the
planetesimal disk. We reduce the base time step size by an additional factor of 4 to the prevent the longitude of perihelia of planetesimals at the inner edge of the disk from drifting by more than the intrinsic spread in $\varpi$ due to the free eccentricity over the course of our integrations.

An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
To start, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of the two-tiered scheme is to properly resolve 
the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/xy.png}
    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
    indicates the position of the giant planet and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
    are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
    and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
\end{center}
\end{figure*}

@@

All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by

\begin{equation}\label{eq:lib_time}
	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| 2p + q \right|}},
\end{equation}

@@

We begin by examining simulations e1m2, e2m2 and e3m2. The positions of the planetesimals in the x-y plane after 5,000 years of integration are 
shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$. The longitude of perihelion of 
the planet is shown by the dashed line. Resonances with the perturbing planet are visible as nonaxisymmetric gaps. Upon close inspection of a 
series of simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and 
\citet{2016ApJ...818..159T} (figure 3). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
time (see Appendix \ref{sec:boley_plot}). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a 
Jupiter mass planet on a circular, coplanar orbit. \citet{2017ApJ...850..103B} used a similar setup. This, the presence of these features seems robust 
to the choice of initial conditions.

The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}. In all cases, 
the 3:1, 2:1 and 5:3 resonances are readily visible as 'spikes' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$). In the 
e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these features from the e1m2 simulation can be 
explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.

Another important effect of the resonances is visible in figure \ref{fig:long_ph}, which shows the orientation of the longitude of perihelia of 
planetesimals in the disk. Inside of the resonances, orbits of planetesimals quickly precess and their orientations are effectively randomized. An 
important point to note is that this strong precession effect quickly disappears beyond the boundaries of the resonance. This turns out to be 
important to explain the nonaxisymmetric structure seen in figure \ref{fig:xy}, which will be addressed in more detail below.

Next, we examine the statistics of collisions resolved in each of the simulations. The 3D positions and velocities of the two colliding bodies are 
recorded to a table at the moment of impact. We derive the Keplerian orbital elements of a collision using these positions and velocities. 
First, we examine the semimajor axis of the first collider, which is shown in figure \ref{fig:coll_hist_a}. During a collision, the 'first' particle is defined 
as the more massive of the two. However, nearly all of the collisions happen between the initial, equal-mass planetesimals. In this case, the 
distinction is set by the collision search algorithm and is rather arbitrary. In all of the plots where we show collision statistics, we have verified that 
using the 'first' or 'second' collider does not qualitatively change any of the features. We find that some of the features present in figure 
\ref{fig:coll_hist_a} in this and subsequent figures are highly sensitive to the number of bins and the location of the bin edges. For this reason, we 
construct a PDF of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
\citep{scikit-learn} package to construct our KDEs. We use a gaussian kernel with a FWHM of 0.02 AU.

@@

We attribute the production of a bump or a dip at certain resonances to changes in the gravitational focusing factor during two-body encounters. 
Closer to the star, the planetesimal disk starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
focusing cross section, which reduces the collision rate from its non-perturbed value. Further out in the disk, where the unperturbed encounter velocity is higher, the gravitational focusing cross section is already minimized. Any additional heating instead acts to simply increase the encounter rate between bodies, which enhances the collision rate. This explains the relative drop in the collision rate near the 3:1 MMR and the relative increase near the 2:1 and 5:3 resonances. Although this could potentially serve as a useful diagnostic of the planetesimal size in a disk (because the mutual escape velocity sets how dynamically hot the bodies can get before gravitational focusing is suppressed), a direct measurement of the semimajor axes of the colliding planetesimals is not possible. Furthermore, as will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution.

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
    \caption{A PDF of the collision rate in each disk as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 AU. In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision rate decreases from its unperturbed value, while an enhancement apepars near the 2:1.\label{fig:coll_hist_a}}
\end{center}
\end{figure}

@@

Operating under this assumption\footnote{As discussed in \cite{2017ApJ...850..103B}, the local generation of second-generation dust is only one 
consideration.  The dust will also evolve spatially due to drag effects, but can also evolve in size or be re-accreted onto planetesimals. For simplicity, 
we focus on local dust sourcing only while acknowledging that subsequent evolution could affect the morphology.}, a map of the relative concentration 
of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. 
Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth of 0.02 AU to assemble the collision locations into a radial distribution. Most 
strikingly, the bump that was present near the 2:1 resonance is no longer visible in cylindrical distance space, although it suddenly appears again in 
the e3m2 simulation. The dip that is visible near the 3:1 MMR also becomes a bump in the highest eccentricity case. To determine how the resonant 
bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and 
between $3.2 < a < 3.35$ AU (near the 2:1 resonance), which is shown by the dashed curve. Qualitatively, none of the bump or dip features present 
are removed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become smeared out in 
cylindrical distance space due to the large spread in eccentricity and orbital orientation.

@@

Although the nonaxisymmetric pileup of bodies near the edges of resonances has been seen previously 
\citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens, which we will try to provide here. As 
mentioned in section \ref{sec:dynamics}, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the 
outside. Following the pendulum analogy, this is equivalent to approaching the point where the pendulum becomes suspended in the vertical position. 
When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of 
conjunction \citep{1976ARA&A..14..215P}.  This is the basic mechanism that causes isolated resonances to be stable. Inside of resonance, the critical 
angle librates about some value and this configuration is maintained. Just outside of resonance, however, the critical angle slowly drifts away, with the 
drift direction changing sign across the resonance. The net result of this is that bodies just outside of the resonance experience a torque from that 
planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the disk 
slowly destroys the configuration over part of an orbit. As the planet passes by, adjacent planetesimals near the resonance edges temporarily align 
themselves in this configuration. This explains why the concentration of planetesimals appears to `follow' the planet.

>>>>

Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure. Features such as gaps and asymmetries 
\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
diagnostics for the physical processes that drive the evolution of the disks. In many gas-rich systems, these gap features are argued to indicate the 
presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
interactions can have strong effects on the resulting morphologies
\citep{2018ApJ...866..110D}. In gas-poor/debris systems, a giant
planet perturber can also influence 
the structure of the dust continuum emission. For example, a misaligned giant planet can produce nonaxisymmetric features such as warps 
\citep{2001A&A...370..447A}, highly eccentric perturbers can produce structures through secular interactions 
\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}, and mean motion resonances (MMRs) can open gaps
\citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

@@

This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive the evolution 
of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:sims} we provide an overview of the N-body code 
used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses 
and eccentricities. Section \ref{sec:results} presents the results of these simulations, and we use the collision statistics to generate synthetic dust 
emission profiles that would be detected with observing facilities like ALMA. Next, we show in section \ref{sec:constrain} that a characteristic bump 
or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
planet. We discuss the potential of using this feature to place upper
or lower limits on the mass and eccentricity of the planet and conclude in section 
\ref{sec:conclusions}.

@@

The most direct and widespread effect that a giant planet perturber will have on a planetesimal disk is through secular forcing of the 
eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time-independent 
forced value, given by \citep{1999ApJ...527..918W} as

@@

\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, 
respectively. $e_{g}$ and $\varpi_{g}$ are the eccentricity and
longitude of pericenter of the giant planet, and $b^{j}_{s} (\alpha)$ is a 
Laplace coefficient given by \citep{2000ssd..book.....M} as

@@

\noindent where $\lambda = \varpi + M$ is the mean longitude of a
body, with $M$ being the mean anomoly. For bodies in resonance, the critical angle will librate around an 
equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
pendulum. Variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{2000ssd..book.....M}. An important 
point to note, which we will come back to later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of 
the $\phi$. For second and higher order resonances, the maximum libration width is given by
% TRQ: there should be a reference (or references) for the equations
% below.  Perhaps something like "Below we derive the libration widths
% following Murray & Dermott, chapter XX.

@@

\noindent where $n$, $a$ and $e$ are the mean motion, semimajor axis and eccentricity of the unperturbed body. $C_{r}$ is a constant defined by 
$m'/m_{c} n \alpha f_{d}(\alpha)$, where $\alpha$ = $a/a'$ and $f_{d}$ is the resonant part of the disturbing function. For an interior second-order 
resonance,

@@

In total, five simulations are run, which are listed in table
\ref{tab:sims}. The first
% TRQ: second?
is a ``nominal'' case, in which the perturbing planet's mass and 
eccentricity are set to that of Jupiter's. In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the 
eccentricity (mass) is held at the nominal value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The 
planetesimal disk extends from 2.2 to 3.8 AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU 
and the 3:1 at 2.5 AU. The planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}

@@

For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/
G M_{\odot}}$. All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr. This is roughly 3\% of an orbital dynamical time at 
the inner edge of the planetesimal disk. From numerical tests with {\sc ChaNGa}, we have found that this time step size preserves 
the symplectic nature of the integration without being too computationally expensive. Although using $\Delta T$ = 0.01 yr keeps the 
integration symplectic, we find that a small amount of artificial
precession is produced.
% TRQ: should we say why?
This is most noticeable at the inner edge of the
planetesimal disk.
% TRQ: so are all particles on a base timestep of 0.0025 yr?
We reduce the base time step size by an additional factor of 4 to the prevent the longitude of perihelia of planetesimals at the inner edge of the disk from drifting by more than the intrinsic spread in $\varpi$ due to the free eccentricity over the course of our integrations.

An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
To start, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
placed on a time step that is a factor of 16 smaller than the orbital
time step.
% TRQ: this shorter timestep is still larger than the planetesimal
% dynamical time; is this a problem?
The purpose of the two-tiered scheme is to properly resolve 
the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/xy.png}
    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
    indicates the position of the giant planet, and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
    are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
    and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
\end{center}
\end{figure*}

@@

All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by
% TRQ: again cite book for this.
\begin{equation}\label{eq:lib_time}
	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| 2p + q \right|}},
\end{equation}

@@

We begin by examining simulations e1m2, e2m2 and e3m2. The positions of the planetesimals in the x-y plane after 5,000 years of integration are 
shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$. The longitude of perihelion of 
the planet is shown by the dashed line. Resonances with the perturbing planet are visible as nonaxisymmetric gaps. Upon close inspection of a 
series of simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and 
\citet{2016ApJ...818..159T} (figure 3). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
time (see Appendix \ref{sec:boley_plot}). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a 
Jupiter mass planet on a circular, coplanar
orbit. \citet{2017ApJ...850..103B} used a similar setup.
Thus, the presence of these features seems robust 
to the choice of initial conditions.

The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}. In all cases, 
the 3:1, 2:1 and 5:3 resonances are readily visible as ``spikes'' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$). In the 
e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these features from the e1m2 simulation can be 
explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.

Another important effect of the resonances is visible in figure \ref{fig:long_ph}, which shows the orientation of the longitude of perihelia of 
planetesimals in the disk. Inside of the resonances, orbits of planetesimals quickly precess, and their orientations are effectively randomized. An 
important point to note is that this strong precession effect quickly disappears beyond the boundaries of the resonance. This turns out to be 
important to explain the nonaxisymmetric structure seen in figure \ref{fig:xy}, which will be addressed in more detail below.

Next, we examine the statistics of collisions resolved in each of the simulations. The 3D positions and velocities of the two colliding bodies are 
recorded in a table at the moment of impact. We derive the Keplerian orbital elements of a collision using these positions and velocities. 
First, we examine the semimajor axis of the first collider, which is shown in figure \ref{fig:coll_hist_a}. During a collision, the ``first'' particle is defined 
as the more massive of the two. However, nearly all of the collisions happen between the initial, equal-mass planetesimals. In this case, the 
distinction is set by the collision search algorithm and is rather arbitrary. In all of the plots where we show collision statistics, we have verified that 
using the ``first'' or ``second'' collider does not qualitatively change any of the features. We find that some of the features present in figure 
\ref{fig:coll_hist_a} in this and subsequent figures are highly sensitive to the number of bins and the location of the bin edges. For this reason, we 
construct a PDF of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
\citep{scikit-learn} package to construct our KDEs. We use a gaussian kernel with a FWHM of 0.02 AU.

@@

We attribute the production of a bump or a dip at certain resonances to changes in the gravitational focusing factor during two-body encounters. 
Closer to the star, the planetesimal disk starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
focusing cross section, which reduces the collision rate from its
non-perturbed value. Further out in the disk, where the unperturbed
encounter velocity is higher, the gravitational focusing cross section
is already minimized. Any additional heating instead acts to simply
increase the encounter rate between bodies, which enhances the
collision rate. This explains the relative drop in the collision rate
near the 3:1 MMR and the relative increase near the 2:1 and 5:3
resonances. Although this could potentially serve as a useful
diagnostic of the planetesimal size in a disk (because the mutual
escape velocity sets how dynamically hot the bodies can get before
gravitational focusing is suppressed), a direct measurement of the
semimajor axes of the colliding planetesimals is not
possible. Furthermore, as we will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution.

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
    \caption{A PDF of the collision rate in each disk as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 AU. In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision rate decreases from its unperturbed value, while an enhancement appears near the 2:1.\label{fig:coll_hist_a}}
\end{center}
\end{figure}

@@

Operating under this assumption\footnote{As discussed in \cite{2017ApJ...850..103B}, the local generation of second-generation dust is only one 
consideration.  The dust will also evolve spatially due to drag effects, but can also evolve in size or be re-accreted onto planetesimals. For simplicity, 
we focus on local dust sourcing only while acknowledging that subsequent evolution could affect the morphology.}, a map of the relative concentration 
of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. 
Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 AU to assemble the collision locations into a radial distribution. Most 
strikingly, the bump that was present near the 2:1 resonance is no longer visible in cylindrical distance space, although it suddenly appears again in 
the e3m2 simulation. The dip that is visible near the 3:1 MMR also becomes a bump in the highest eccentricity case. To determine how the resonant 
bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and 
between $3.2 < a < 3.35$ AU (near the 2:1 resonance), which is shown by the dashed curve. Qualitatively, none of the bump or dip features present 
are removed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become smeared out in 
cylindrical distance space due to the large spread in eccentricity and orbital orientation.

@@

Although the nonaxisymmetric pileup of bodies near the edges of resonances has been seen previously 
\citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens, which we will try to provide here. As 
mentioned in section \ref{sec:dynamics}, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the 
outside. Following the pendulum analogy, this is equivalent to
approaching the point where the pendulum becomes suspended in the
vertical position
% TRQ addition
at top dead center. 
When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of 
conjunction \citep{1976ARA&A..14..215P}.  This is the basic mechanism that causes isolated resonances to be stable. Inside of resonance, the critical 
angle librates about some value and this configuration is maintained. Just outside of resonance, however, the critical angle slowly drifts away, with the 
drift direction changing sign across the resonance. The net result of this is that bodies just outside of the resonance experience a torque from that 
planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the disk 
slowly destroys the configuration over part of an orbit. As the planet passes by, adjacent planetesimals near the resonance edges temporarily align 
themselves in this configuration. This explains why the concentration of planetesimals appears to `follow' the planet.
